---
title: "P2 Report"
output: html_document
date: "2022-11-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Hillary Chen (chenhil1@uw.edu), Emma Hong (emmah36@uw.edu), Julia Kharchenko (juliak24@uw.edu) , Truc Quynh Nguyen (TQ) (truc1976@uw.edu) 
( Write Intro )

```{r cars}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE,echo=FALSE,message=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r, echo=FALSE,warning=FALSE,echo=FALSE,message=FALSE}
source("../source/R_Race_and_Age_Chart_#3.R")
bar_chart
```

We included a stacked bar chart detailing the racial background of those who died from COVID-19 per age group to identify the intersectionality between many marginalized groups when it comes to COVID-19 related deaths (e.g. how Hispanic milennials compare to the Black elderly population). By creating this chart, we can see that the older a person is, the more likely they are to die from COVID-19, and that the proportion of those dying from COVID-19 who are Non-Hispanic White are larger than other groups, likely because they make up a larger population as a whole. However, Hispanic and Non-Hispanic Black individuals tend to die from COVID-19 in larger proportions at slightly younger ages e.g. from 50-64 years, which is an interesting feature to look into and analyze further.

```{r, echo=FALSE,warning=FALSE,echo=FALSE,message=FALSE}
source("../source/R_Race_Pie_Chart_#1.R")
Pie_Chart_Covid_Deaths
```
We made a pie chart in order to see how different races has been affected by COVID-19. By the results of this visual, we were able to find out that Non-Hispanic White group made up 84.7% of this pie chart. This means that they were the most affected by COVID-19 versus other races. By making a pie chart, we were visually able to see the data as a fractional part of a whole which can be a straight forward and effect communication tool for even an uniformed reader. 
